% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Levon Dovlatyan}
% \address used twice to have two lines of address
\address{4708 \#203 Cherokee st, College Park, MD, 20740}
\address{email: levondov@umd.edu | phone: (818) 319 3797}

 
\begin{resume}
 
 
\section{EDUCATION} {\sl Ph.D,} Physics \\
                    University of Maryland, College Park, MD,
                    expected May 2022 \\
                    Specialization: Accelerator and Beam Physics


                {\sl B.S,} Engineering Physics \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                UC Berkeley, Berkeley, CA, 
                December 2015 \\
 
\section{RELEVANT \\ WORK \\ EXPERIENCE} 
                UMER group, University of Maryland \\
                {\sl Graduate Student} \hfill 2016-Present \\
                Research Advisor: Prof. Rami Kishek
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Developing simulations and experiments to better study the beam dynamics in UMER.
                 \item Improving control systems (hardware \& software).
                 \item Assisting with various engineering and physics projects related to UMER's operation.
                \end{itemize}
 
                Advanced Light Source (ALS), Lawrence Berkeley National Lab (LBNL) \\
                {\sl Undergraduate Researcher} \hfill 2014-2015 \\
                Advisors: Greg Portmann and Dr. David Robin
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Researching lattice diagnostic techniques with TbT beam position monitors.
                 \item Upgrading and improving control room operational software.
                 \item Assisted in normal accelerator physics operations.
                 \end{itemize} 
                 
                BESSY II,  Helmholtz-Zentrum Berlin (HZB) \\
                {\sl Undergradute Researcher} \hfill Summer 2014\\
                Advisors: Dr. Markus Ries and Dr. Paul Goslawski
                  \begin{itemize} \itemsep -2pt %reduce space between items
                   \item Developed control room software to help assist with operations and physics experiments.
                   \item Built the optical path for a new streak camera at the physics test beamline and helped take measurements afterwards.
                   \item Assisted in normal accelerator physics operations.
                   \end{itemize} 
 
\section{TEACHING}  University of Maryland \hfill 2016-Present \\
                    {\sl Graduate Instructor} \\
                    \begin{itemize} \itemsep -2pt
                    \item Math 113 (Fall 2017) - College Algebra and Trigonometry
                    \end{itemize}                    
                    {\sl Graduate Teaching Assistant} \\
                    \begin{itemize} \itemsep -2pt
                    \item Physics 132 (Spring 2017) - Fundamentals of Physics for Biologists II
                    \item Physics 132 (Fall 2016) - Fundamentals of Physics for Biologists II
                    \end{itemize}
                    Project GRAD Los Angeles \hfill 2012-2013 \\
                    {\sl Teacher}
                    \begin{itemize} \itemsep -2pt
                    \item Worked on-campus at middle and high schools around the San Fernando Valley.
                    \item Facilitated and taught several periods of class three days a week
                    \item Worked in after school and weekend tutoring activities
                    \end{itemize}
                    

\section{RELEVANT COMPUTER SKILLS} Languages: C++, Python, Matlab, Lua, Java, Bash \hfill Type Setting: \LaTeX \\
                          Web: Full-Stack developer \hfill OS: Linux (Ubuntu), Windows \\
                          Specialized: EPICS, Elegant, Django, MML \hfill Version Control: Git, Mercurial
\section{PRESENTATIONS} \hfill \\
                L. Dovlatyan, G. Portmann, "Measuring energy dependent tune shifts during RF failures." ALS accelerator physics group meeting, LBNL B 80-234-CR, Berkeley, CA. April 22 2015 \\ \\
                L. Dovlatyan, "Applications of TbT BPM data." ALS accelerator physics group meeting,
LBNL B 80-234-CR, Berkeley, CA. July 22 2015.
 

\end{resume}
\end{document}







